---
title: "ASSIGNMENT3"
author: "rajiv"
date: "3/6/2022"
output: pdf_document
---

```{r}

ULbank = read.csv("C:\\Users\\rdevi\\Downloads\\UniversalBank.csv")
View(ULbank)

#loading required libraries

```{r}

library(caret)
library(ISLR)
library(e1071)

#converting variables

```{r}

ULbank$Personal.Loan = factor(ULbank$Personal.Loan)
ULbank$Online = factor(ULbank$Online)
ULbank$CreditCard = factor(ULbank$CreditCard)

```{r}

set.seed(64060)

#spliting data into training 60% and validatio 40%

Train_Index = createDataPartition(ULbank$Personal.Loan, p = 0.6, list = FALSE)
Train.df = ULbank[Train_Index,]
Validation.df = ULbank[-Train_Index]

#Task-A. Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable.

```{r}

mytable = xtabs(~ CreditCard+Personal.Loan+Online,data = Train.df)
ftable(mytable)

#Task-B.Consider the task of classifying a customer who owns a bank credit card and is actively using online banking services. Looking at the pivot table, what is the probability that this customer will accept the loan offer? [This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)].

```{r}

59/(479+59)

#Task-C.Create two separate pivot tables for the training data. One will have Loan (rows) as a unction of Online (columns) and the other will have Loan (rows) as a function of CC. 

```{r}

table(Personal.Loan = Train.df$Personal.Loan, CreditCard = Train.df$CreditCard)
table(Personal.Loan = Train.df$Personal.Loan, Online = Train.df$Online)
table(Personal.Loan = Train.df$Personal.Loan)

#Task-D.Compute the following quantities [P(A | B) means “the probability ofA given B”]: 

#1. P(CC = 1 | Loan = 1)

```{r}

93/(93+195)

#2. P(Online = 1 | Loan = 1) 

```{r}

179/(179+109)

#3. P(Loan = 1)

```{r}

288/(288+2712)

#4. P(CC = 1 | Loan = 0)

```{r}

788/(788+1924)

#5 P(Online = 1 | Loan = 0)

```{r}

1631/(1631+1081)

#6 P(Loan = 0) 

```{r}

2712/(2712+288)

#Task-E.Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1, Online = 1).

```{r}

(0.3229167*0.6215278*0.096)/((0.3229167*0.6215278*0.096)+(0.29056052*0.6014012*0.904))

# The value obtained from naivebayes probability is 0.1087106

#Task-F.Compare this value with the one obtained from the pivot table in (B). Which is a more accurate estimate ?

##The value from the pivot table is 0.1096654 and the naive bayes probability is 0.1087106 and these values are almost similar.Pivot table value is more accurate.


#Task-G.Which of the entries in this table are needed for computing P(Loan = 1 | CC = 1, Online = 1)? Run naive Bayes on the data. Examine the model output on training data, and find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1). Compare this to the number you obtained in (E).

```{r}

nb.model = naiveBayes(Personal.Loan~CreditCard+Online, data = Train.df)
To_Predict = data.frame(CreditCard = 1 , Online = 1)
predict(nb.model,To_Predict,type = 'raw') 



